Project

### 2022-04-01 Project/DraftR.Rmd
Update DraftR.Rmd

GitHub Link:

@@

## Data Check and Modification
```{r}
sapply(clim, class)
```
```{r}
#d.snowpack.10.11=days with snowpack winter 2010-2011
#wTmin.10.11=minimum temperature winter (C) at plant height 2010-2011
#Dec.FebTav.10.11=mean temperature at plant height from Dec1st 2010 - Feb 28th 2011
#d.grows.11=# days in growing season 2011 (start / end of gorwing season determined by sustained snow or frost)
#GDD.grows.11=# growing degree days (Tbase=10C, Tmax capped at 30C) in growing season of 2011
#GDD.yr.11=# growing degree days in 2011 (ie not truncated to estimated growing season)
#avmaxminTJuly.11=mean July 2011 temperature (C) calculated from daily min and max T: mean(July1stmin + July1stmax + July2ndmin + July2ndmax + ... July31stmi + July31stmax)
#avTJuly.11=mean July 2011 temperature (C) calculated from raw data (ie >2 measurements per day)

#hence, convert the above columns into numeric variables
cols.num <- c("d.snowpack.11.12", "wTmin.11.12", "Dec.FebTav.11.12", "d.grows.12", "GDD.grows.12", "GDD.yr.12", "avmaxminTJuly.12", "avTJuly.12", "GDD.grows.13", "GDD.yr.13", "avmaxminTJuly.13", "avTJuly.13", "d.snowpack.13.14", "wTmin.13.14", "Dec.FebTav.13.14")
clim[cols.num] <- sapply(clim[cols.num],as.numeric)
sapply(clim, class)
head(clim)
```
```{r}
#use 'melt' to convert the 'clim' data.frame into long format in which 'transect' and 'site' are identifier variables, while the other are considered as the measured variables.
clim.sea <- melt(clim, id.vars = c('transect','site'), measure.vars = 3:29)
head(clim.sea)
```

>>>>

GitHub Link: https://github.com/zazauwu/432_Group5

@@

## Data Check and Modification
```{r}
sapply(clim, class)
```
```{r}
#variable explanation:
  #d.snowpack.10.11 = days with snowpack winter 2010-2011
  #wTmin.10.11 = minimum temperature winter (C) at plant height 2010-2011
  #Dec.FebTav.10.11 = mean temperature at plant height from Dec1st 2010 - Feb 28th 2011
  #d.grows.11 = # days in growing season 2011 (start / end of gorwing season determined by sustained snow or frost)
  #GDD.grows.11 = # growing degree days (Tbase=10C, Tmax capped at 30C) in growing season of 2011
  #GDD.yr.11 = # growing degree days in 2011 (ie not truncated to estimated growing season)
  #avmaxminTJuly.11 = mean July 2011 temperature (C) calculated from daily min and max T: 
      #mean(July1stmin + July1stmax + July2ndmin + July2ndmax + ... July31stmi + July31stmax)
  #avTJuly.11 = mean July 2011 temperature (C) calculated from raw data (ie >2 measurements per day)

#hence, convert the above columns into numeric variables
cols.num <- c("d.snowpack.11.12", "wTmin.11.12", "Dec.FebTav.11.12", "d.grows.12", "GDD.grows.12", "GDD.yr.12", "avmaxminTJuly.12", "avTJuly.12", "GDD.grows.13", "GDD.yr.13", "avmaxminTJuly.13", "avTJuly.13", "d.snowpack.13.14", "wTmin.13.14", "Dec.FebTav.13.14")
clim[cols.num] <- sapply(clim[cols.num],as.numeric)
sapply(clim, class)
head(clim)
```
```{r}
#use 'melt' to convert the 'clim' data.frame into long format in which 'transect' and 'site' are identifier variables, while the other are considered as the measured variables.
clim.sea <- melt(clim, id.vars = c('transect','site'), measure.vars = 3:29)
head(clim.sea)
```
```{r}
#use regular expression 'grepl' and 'gsub' to add 'year' column and remove date label in the 'variable' column
clim.sea$year <- ifelse(grepl('10.11', long$variable), 
                    'winter 10-11',
                    ifelse(grepl('11.12', long$variable), 
                           'winter 11-12',
                           ifelse(grepl('12.13', long$variable), 
                                  'winter 12-13',
                                  ifelse(grepl('13.14', long$variable), 
                                         'winter 13-14',
                                         ifelse(grepl('grows.11|July.11|yr.11', long$variable), 
                                                'year 2011',
                                                ifelse(grepl('grows.12|July.12|yr.12', long$variable), 
                                                       'year 2012',
                                                       ifelse(grepl('grows.13|July.13|yr.13', long$variable), 
                                                              'year 2013',
                                                              NA)))))))

clim.sea <- clim.sea %>%
  mutate(variable = gsub(".(\\d).*", "\\2", variable))
